\Huge{Machine Learning} \\ \LARGE Nature's Quest: Deep Learning Exploration of Global Plant Traits from Images and Geodata

### 2024-03-07 paper/paper.tex
basic paper outline and some formatting changes

\documentclass[12pt,a4paper,oneside]{article}
%\documentclass[12pt,a4paper,oneside,twocolumn]{article}

% Bibliography & Language
\usepackage[english]{babel} % Language-specific stuff, f.i. hyphenation
\usepackage{csquotes} % Allows for quotes - recommended by babel
\usepackage[style=ieee, sorting=nyt, urldate=long, date=long, backend=biber]{biblatex}
\addbibresource{sources.bib}

% General document
\usepackage[useregional]{datetime2} % Date
\usepackage{titling} % Allows for multiple titles (info sheet)
\usepackage{libertinus} % Fonts
\usepackage[margin=3cm]{geometry} % Custom margins
\usepackage{parskip} % Removes indentation at start of paragraph, add space between them
\usepackage[normalem]{ulem} % Underlining
\useunder{\uline}{\ul}{}
\usepackage[htt]{hyphenat} % Hyphenation for monospace text
\usepackage{todonotes} % Add todos
\usepackage{blindtext} % lorem ipsum, blind text

% Graphics
\usepackage{graphicx} % Graphics extended
\usepackage{hyperref} % Refer to things, including URLs
\usepackage{float} % Allows for H float option ("here")
\usepackage{caption} % allows for centered figure caption justification

@@

\title{\Huge{Machine Learning}\\\LARGE TODO: Title goes here}
\author{
Kai E. Niermann \and
Dávid Miklo \and 
Trix Taicet \and
Red Kaláb \and
Conner Dassen
}
\date{\DTMusedate{date}}
\begin{document}
\maketitle

\blinddocument

\include{info_sheet.tex}
\end{document}

>>>>

\documentclass[12pt,a4paper,oneside]{article}
%\documentclass[12pt,a4paper,oneside,twocolumn]{article}
\usepackage{pagestyle}
\usepackage{codestyle}

@@

\title{
    \Huge{Machine Learning} \\ \LARGE 
    Nature's Quest: Deep Learning Exploration of Global Plant Traits from Images and Geodata
}
\author{
Kai E. Niermann \and
Dávid Miklo \and 
Trix Taicet \and
Red Kaláb \and
Conner Dassen
}
\date{\DTMusedate{date}}
\begin{document}
\maketitle

% \lstinputlisting[firstline=10, lastline=13]{code/sample_script.py}

\begin{abstract}
    % Abstract content goes here
\end{abstract}

\section{Introduction}

\section{Literature review}

\section{Data processing}

\section{Method}

\subsection{Model design}

\subsection{Model evaluation}

\subsection{Results}

\section{Discussion}

\section{Conclusion}

\end{document}
